NFI process: grid-based sampling

### 2024-07-05 NFI_method.Rmd
NFI better

---
title: "NFI process: grid-based sampling"
output: html_document
date: "2024-07-05"
---

@@

```{r}
plot(x = random_points$x, y = random_points$y, xlab = "", ylab = "", main = "Random points", panel.first=grid())
```
Figure 1.**Points sampled following a grid over the whole territory**.

@@

```{r}
# Total volume of trees
a <- mapply(circle3_nb, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
est_init_vol <- sum(a/p)
rm(a)
cat("Volume of the forest:", sum(trees$v), "\nEstimation of the volume of the forest:", est_init_vol)
```

@@

  nboot <- length(df_boot)/2
  vec_est <- c()
  for (c in 1:nboot) {
    a <- mapply(circle3_nb, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6))
    vec_est <- append(vec_est, sum(a/p))
  }
  vec_est <- sort(vec_est)
  return(vec_est)
  # Vector with one estimation for each sample
}
```

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot_nb <- est_boot(df_init, df_boot, circle3_nb)
```

@@

```{r}
print("Two intervals for the number of trees:\n")
res_nb <- ci_perc(est_init_nb,est_boot_nb)
```

```{r}
# Visualizing the density, the interval and the first estimation
plot(density(est_boot_nb), xlab="Number of trees",ylab="", main = "Distribution based on bootstrap", las = 1)
abline(v=res_nb[2], col="blue")
abline(v=res_nb[3], col="blue")
abline(v=est_init_nb*2 - res_nb[3], col="green")
abline(v=est_init_nb*2 - res_nb[2], col="green")
abline(v=est_init_nb, col="red")
abline(v=nrow(trees), col="black")
```
Figure 2.**Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).

@@

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot_vol <- est_boot(df_init, df_boot, circle3_vol)
```

```{r}
print("Two intervals for the volume of the forest:\n")
res_nb <- ci_perc(est_init_nb,est_boot_vol)
```

```{r}
# Visualizing the density, the interval and the first estimation
plot(density(est_boot_nb), xlab="Volume of the forest",ylab="", main = "Distribution based on bootstrap", las = 1)
abline(v=res_vol[2], col="blue")
abline(v=res_vol[3], col="blue")
abline(v=est_init_vol*2 - res_vol[3], col="green")
abline(v=est_init_vol*2 - res_vol[2], col="green")
abline(v=est_init_vol, col="red")
abline(v=sum(trees$v), col="black")
```
Figure 3.**Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).

>>>>

---
title: "NFI process: grid-based sampling"
output:
  pdf_document: default
  html_document: default
date: "2024-07-05"
---

@@

```{r}
plot(x = random_points$x, y = random_points$y, xlab = "", ylab = "", main = "Random points", panel.first=grid(), las = 1)
```
Figure 1. **Points sampled following a grid over the whole territory**.

@@

```{r}
# Total volume of trees
a <- mapply(circle3_vol, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
est_init_vol <- sum(a/p)
rm(a)
cat("Volume of the forest:", sum(trees$v), "\nEstimation of the volume of the forest:", est_init_vol)
```

@@

  nboot <- length(df_boot)/2
  vec_est <- c()
  for (c in 1:nboot) {
    a <- mapply(fun, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6))
    vec_est <- append(vec_est, sum(a/p))
  }
  vec_est <- sort(vec_est)
  return(vec_est)
  # Vector with one estimation for each sample
}
```

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot_nb <- est_boot(df_boot, circle3_nb)
```

@@

```{r}
print("Two intervals for the number of trees:")
res_nb <- ci_perc(est_init_nb,est_boot_nb)
```

```{r}
# Visualizing the density, the interval and the first estimation
plot(density(est_boot_nb), xlab="Number of trees",ylab="", main = "Distribution based on bootstrap", las = 1)
abline(v=res_nb[2], col="blue")
abline(v=res_nb[3], col="blue")
abline(v=est_init_nb*2 - res_nb[3], col="green")
abline(v=est_init_nb*2 - res_nb[2], col="green")
abline(v=est_init_nb, col="red")
abline(v=nrow(trees), col="black")
```
Figure 2. **Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).

@@

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot_vol <- est_boot(df_boot, circle3_vol)
```

```{r}
print("Two intervals for the volume of the forest:")
res_vol <- ci_perc(est_init_vol,est_boot_vol)
```

```{r}
# Visualizing the density, the interval and the first estimation
plot(density(est_boot_vol), xlab="Volume of the forest",ylab="", main = "Distribution based on bootstrap", las = 1)
abline(v=res_vol[2], col="blue")
abline(v=res_vol[3], col="blue")
abline(v=est_init_vol*2 - res_vol[3], col="green")
abline(v=est_init_vol*2 - res_vol[2], col="green")
abline(v=est_init_vol, col="red")
abline(v=sum(trees$v), col="black")
```
Figure 3. **Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).
